General constraints on magic distillation protocols from statistical mechanics

### 2021-06-03 magic_paper.tex
Typo...issue with entropy to free energy not clear to me right now.
Final comment for the day.

Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
This should provide relative majorization monotones from which we can obtain distillation bounds, such as
\begin{equation}
R \le \frac{H_\alpha(\tau) - H_\alpha (\rho)}{H_\alpha(\tau') - H_\alpha (\rho')}.
\end{equation}
\ddd{[To be checked]}
\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}

>>>>

Therefore if we have a Schur-Concave function $f(\x)$ for majorization of quasi-distributions then we can define a monotonic function for relative majorization via composition with $\Gamma_{\mathbf{a}}$ and its inverse.
This should provide relative majorization monotones from which we can obtain distillation bounds, such as
\begin{equation}
R \le \frac{F_\alpha(\tau) - F_\alpha (\rho)}{F_\alpha(\tau') - F_\alpha (\rho')}.
\end{equation}
\ddd{[To be checked...transition from entropies to free energies less obvious from this route...needs reflection]}

This is probably all we need to show:
\begin{equation}
H_\alpha(\Gamma_{\mathbf{a}}(\p)) = D_\alpha(\p ||\r),
\end{equation}
where we define the Renyi relative entropy
\begin{equation}
D_\alpha (\p || \r) := \frac{1}{\alpha -1} \log \sum_i p_i^\alpha q_i^{1-\alpha}.
\end{equation}
This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.
\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}
